---
title: "2050"
listing:
  contents: posts
  sort: "date desc"
  type: default
  categories: true
  sort-ui: false
  filter-ui: false
page-layout: full
title-block-banner: true
---

## 2050 DATABASE {style="color: blue"}

```{r}
#| label : setup

library(tidyverse) # Tidy data processing
library(plotly)
library(ggformula) # Formula based plots
library(mosaic) # Data inspection and Statistical Inference
library(broom) # Tidy outputs from Statistical Analyses
library(infer) # Statistical Inference, Permutation/Bootstrap
library(patchwork) # Arranging Plots
library(ggprism) # Interesting Categorical Axe
```

### DATASET CONSIDERATIONS {style="color: blue"}

-   Number of people = 1000

-   Age = Legally, people above 21 onward are allowed to have the bio-computer in their body, since it is the year 2050, the global population is projected to reach 9.7 B, with a significant increase in the elderly age group thus the median will shift from 31 (current) to 36 approx.

-   Profession = Currently have included 4 profession across various industries such as agriculture, engineering, healthcare and transport according to their need in 2050.

-   Social connection = Essentially is the number of people a certain person knows.

-   Access to healthcare = Basically how easy it is for them to get proper healthcare.

-   Resource availability = Again, takes into consideration how much a person has access to resources ranging from 20-100.

```{r}
set.seed(123)

n <- 1000

Age <- round(rnorm(n, mean = 36, sd = 15)) 
Age[Age < 21] <- 21  

Gender <- sample(c("Male", "Female"), n, replace=TRUE, prob=c(0.5, 0.5))  # Equal distribution of Male and Female

Professions <- c("Farmer", "Engineer", "Doctor", "Driver")
Profession <- sample(Professions, n, replace = TRUE, prob = c(0.2, 0.5, 0.2, 0.1))  

Resources <- runif(n, min = 20, max = 100)

HealthcareAccess <- runif(n, min = 0, max = 1)

BioComputerUser <- sample(c("Yes", "No"), n, replace=TRUE, prob=c(0.3, 0.7))

# Combine everything into a dataframe
society_2050 <- data.frame(
  Age,
  Gender,
  Profession,
  Resources,
  HealthcareAccess,
  BioComputerUser
)

# Check the first few rows
head(society_2050)
```

```{r}
write.csv(society_2050, "society_2050.csv", row.names=FALSE)
```

```{r}
getwd()
```

### DATA MUNGING {style="color: blue"}

```{r}
society_2050 <- society_2050 %>%
  mutate(
    Age = as.integer(Age),               # Convert Age to integer
    Profession = as.factor(Profession),    # Convert Profession to factor
    Resources = as.numeric(Resources),    # Convert Resources to numeric
    HealthcareAccess = as.numeric(HealthcareAccess),  # Convert HealthcareAccess to numeric
    BioComputerUser = as.factor(BioComputerUser)  # Convert BioComputerUser to factor
  )

# Check the structure of the modified dataset
glimpse(society_2050)
```

### DATA DICTIONARY {style="color: blue"}

### 

#### BOX PLOT

-   The boxplot showcases how resources are distributed for doctors and engineers, to understand if one profession has consistently higher or lower resources than the other.

-   The plot shows the range and outliers that are outside the typical range.

```{r}
# Filter the dataset for Doctors and Engineers
subset_profession <- society_2050[society_2050$Profession %in% c("Doctor", "Engineer"), ]

# Create the box plot
ggplot(subset_profession, aes(x = Profession, y = Resources, fill = Profession)) +
  geom_boxplot() +
  labs(title = "Resource Distribution: Doctors vs Engineers",
       x = "Profession",
       y = "Resource Availability") +
  scale_fill_manual(values = c("Doctor" = "blue", "Engineer" = "purple")) +
  theme_minimal(base_size = 14)

```

```{r}
scatter_plot <- plot_ly(
  data = society_2050,
  x = ~Resources,
  y = ~HealthcareAccess,
  type = "scatter",
  mode = "markers",
  color = ~Profession, # Color by Profession (Engineer, Doctor etc.)
  marker = list(opacity = 0.6)
)

# 2D Histogram (Density Plot)
hist2d_plot <- plot_ly(
  data = society_2050,
  x = ~Resources,
  y = ~HealthcareAccess,
  type = "histogram2d"
)

# Combine both plots vertically
fig <- subplot(scatter_plot, hist2d_plot, nrows = 2, shareX = TRUE, shareY = TRUE)

fig
```

```{r}
set.seed(123)
society_2050$year <- sample(2020:2050, n, replace = TRUE)

fig <- plot_ly(
  data = society_2050, 
  x = ~Age, 
  y = ~Resources, 
  color = ~HealthcareAccess, 
  size = ~ifelse(BioComputerUser == "Yes", 10, 5),
  text = ~paste("Age:", Age, "<br>Resources:", round(Resources, 2), 
                "<br>Healthcare Access:", round(HealthcareAccess, 2), 
                "<br>BioComputer User:", BioComputerUser),
  frame = ~year,  
  type = 'scatter',
  mode = 'markers',
  marker = list(opacity = 0.6),
  hoverinfo = 'text'
)

fig
```
